On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2020-11-13 paper/cav_determinisim_main.tex
Did some updates to plots

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummaryV4.pdf}
    \caption{Summary of results showing maximum deviation for each scenario against different resource utilisation levels. Tests 5 and 6 overlap having almost identical results.}
    \label{ExperimentsStressSummary}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionCG25_V4.pdf}
        \caption{}
        \label{CarsCollisionCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionPrePostV4.pdf}
        \caption{}
        \label{CarsCollisionPrePost}
    \end{subfigure}
    \caption{Vehicle to vehicle collision (test 2) showing (a) mean deviation against simulation time for 25\% resource utilisation and (b) mean deviation pre- and post-collision against resource utilisation. The simulation noise floor is shown in (a) which is the empirical lower limit of deviation for the hardware reported in this study.}
\end{figure*}

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollsionsCG25_V3.pdf}
        \caption{}
        \label{CarsPeopleCollsionsCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollisionPrePostV4.pdf}
        \caption{}
        \label{CarsPeopleCollisionPrePost}
    \end{subfigure}
    \caption{Vehicle to pedestrian collision (test 4) showing (a) maximum deviation against simulation time for 25\% stress and (b) maximum deviation pre- and post-collision for different resource utilisation levels.}
\end{figure*}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/NICE_analysis_summary.pdf}
    \caption{Summary of investigating the effect of NICE priority setting for 0\% and 75\% CPU \& GPU Resource Utilisation.}
    \label{NICEExperimentStressSummary}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummaryV5.pdf}
    \caption{Summary of results showing maximum deviation for each scenario against different resource utilisation levels. Tests 5 and 6 overlap having almost identical results.}
    \label{ExperimentsStressSummary}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionCG25_V4.pdf}
        \caption{}
        \label{CarsCollisionCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionPrePostV5.pdf}
        \caption{}
        \label{CarsCollisionPrePost}
    \end{subfigure}
    \caption{Vehicle to vehicle collision (test 2) showing (a) mean deviation against simulation time for 25\% resource utilisation and (b) mean deviation pre- and post-collision against resource utilisation. The simulation noise floor is shown in (a) which is the empirical lower limit of deviation for the hardware reported in this study.}
\end{figure*}

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollsionsCG25_V3.pdf}
        \caption{}
        \label{CarsPeopleCollsionsCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollisionPrePostV5.pdf}
        \caption{}
        \label{CarsPeopleCollisionPrePost}
    \end{subfigure}
    \caption{Vehicle to pedestrian collision (test 4) showing (a) maximum deviation against simulation time for 25\% stress and (b) maximum deviation pre- and post-collision for different resource utilisation levels.}
\end{figure*}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/NICE_analysis_summary_V3.pdf}
    \caption{Summary of investigating the effect of NICE priority setting for 0\% and 75\% additonal CPU \& GPU resource utilisation.}
    \label{NICEExperimentStressSummary}
\end{figure}
